### 2012-05-10 trunk/GUIErrorDetector/paper/technique.tex
make the number correct

\noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
thread is spawned by the UI thread. Under this assumption,
we ignore all non-UI threads created by the GUI framework
before the UI thread has been initialized. That is, all post-initialization
GUI work occurs in the UI thread. Once the GUI is visible, the
application is driven by events, which are always handled in the UI thread.
We believe this assumption is reasonable, since if a non-UI thread 
spawned during pre-initialization GUI work accesses a GUI object, an exception becomes
immediately apparent and the whole application may abort even before the
GUI is visible. This is highly unlikely for fielded GUI
applications.
}\vspace{1mm}

@@

\textbf{1. Filter Lexically Redundant Reports}. One reported method call
chain can lexically subsume another one. For example, suppose that two
reported method call chains; \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
$\rightarrow$ \CodeIn{c()} and 
\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()},
both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
are two distinct entry methods. The second call chain can
be removed without reducing the error detection capability, since
the first chain reveals the same error and is shorter 
for programmers to interpret.

%\item
\textbf{2. Filter Reports with User-Annotated Methods}. Users are
permitted to explicitly annotate project-specific methods
that will never trigger an error.
%For example, the Android GUI framework provides a utility method 
%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
%before executing the code. If the current thread is not the UI thread,
%this method will be executed on the UI thread via message passing.
%Thus,
A reported method call chain containing an annotated  method
can be safely removed. In our experiments, we produced a list of \filternum
annotated methods for two subjects (Fennec and MyTracks) because they use a customized
pattern to interact with the GUI framework.

@@

\textbf{3. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
We encoded a list of 25 common library calls by proposing
a basic set of library calls that seemed %natural and
generally applicable, based on our programming experience.
We later added other calls we found helpful in analyzing
programs on different GUI frameworks and that we believed would be generally useful.
%We did this only between experiments rather than biasing experiments by tuning
%our tool to specific programs.

\textbf{4. Filter Report with the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
multiple methods that access GUI objects, such as:

\pagebreak[3]
\vspace{-2mm}                   %
\begin{CodeOut}
\begin{alltt}
     public void m() \ttlcb
         accessUIObject1();
         accessUIObject2();
     \ttrcb
\end{alltt}
\end{CodeOut}
\vspace{-2mm}
If method \CodeIn{m()} is invoked by a non-UI thread, method call chains that
only differ in the last few method nodes may be reported separately, such as:

>>>>

\noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
thread is (transitively) spawned by the UI thread. Under this assumption,
we ignore all non-UI threads created by the GUI framework
before the UI thread has been initialized. That is, we assume all post-initialization
GUI work occurs in the UI thread. Once the GUI is visible, the
application is driven by events, which are always handled in the UI thread.
We believe this assumption is reasonable, since if a non-UI thread 
spawned during pre-initialization GUI work accesses a GUI object, an exception becomes
immediately apparent and the whole application may abort even before the
GUI is visible. This is highly unlikely for fielded GUI
applications.
}\vspace{1mm}

@@

\textbf{1. Filter Lexically Redundant Reports}. One reported method call
chain can lexically subsume another one. For example, suppose that two
reported method call chains, \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
$\rightarrow$ \CodeIn{c()} and 
\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()},
both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
are two distinct entry methods. The second call chain can
be removed without missing any errors, since
the first chain reveals the same error and is shorter 
for programmers to interpret.

%\item
\textbf{2. Filter Reports with User-Annotated Methods}. Users are
permitted to explicitly annotate specific methods
that will never trigger an error.
%For example, the Android GUI framework provides a utility method 
%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
%before executing the code. If the current thread is not the UI thread,
%this method will be executed on the UI thread via message passing.
%Thus,
Assuming the user annotations are accurate,
a reported method call chain containing an annotated method
can be safely removed.

In our experiments, 
we produced a list of \filternum annotated methods for two
subjects (MyTracks and Fennec), since they employ a customized pattern
to interact with the GUI framework. For example, in MyTracks, all non-UI
threads are initialized via using the library method \CodeIn{android.os\-.handler.handleCallback}.
This method can be invoked from any thread and will never cause an
invalid thread access error, because it checks whether the current
thread is the UI thread or not before execution. If not,
this method will use safe UI methods to run the code in the UI thread.

% we produced a list of \filternum
%annotated methods for two subjects (Fennec and MyTracks) because they use a customized
%pattern to interact with the GUI framework.

@@

\textbf{3. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when the JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
Our experiments use a list of \libnum such library calls.

\textbf{4. Filter Reports with the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
multiple methods that access GUI objects, such as:

\pagebreak[3]
\vspace{-2mm}                   %
\begin{CodeOut}
\begin{alltt}
     public void m() \ttlcb
         accessUIObject1();
         accessUIObject2();
     \ttrcb
\end{alltt}
\end{CodeOut}
\vspace{-2mm}
If method \CodeIn{m()} is invoked by a non-UI thread, our algorithm will
report method call chains that
only differ in the last few method nodes, such as:
